### 2018-11-03 Paper/app.tex
..
final revision

\subsection{Problem Set-up}
\label{sub:setup}  
The mechanism comprises of 19 reactions including chain reactions,
dissociation/recombination reactions, and formation and consumption
of intermediate species as provided below in Table~\ref{tab:kinetics}.

\begin{table}[htbp]
\renewcommand*{\arraystretch}{1.2}
\begin{center}
\begin{tabular}{llll}
\toprule
Reaction \#     & Reaction &&\\
\bottomrule
$\mathcal{R}_1$ & H + O$_2$          & $\rightleftharpoons$ & O + OH \\
$\mathcal{R}_2$ & O + H$_2$          & $\rightleftharpoons$ & H + OH \\
$\mathcal{R}_3$ & H$_2$ + OH         & $\rightleftharpoons$ & H$_2$O + H \\
$\mathcal{R}_4$ & OH + OH            & $\rightleftharpoons$ & O + H$_2$O \\
$\mathcal{R}_5$ & H$_2$ + M          & $\rightleftharpoons$ & H + H + M \\
$\mathcal{R}_6$ & O + O + M          & $\rightleftharpoons$ & O$_2$ + M \\
$\mathcal{R}_7$ & O + H + M          & $\rightleftharpoons$ & OH + M \\
$\mathcal{R}_8$ & H + OH +M          & $\rightleftharpoons$ & H$_2$O + M \\
$\mathcal{R}_9$ & H + O$_2$ + M      & $\rightleftharpoons$ & HO$_2$ + M \\
$\mathcal{R}_{10}$ & HO$_2$ + H      & $\rightleftharpoons$ & H$_2$ + O$_2$ \\
$\mathcal{R}_{11}$ & HO$_2$ + H      & $\rightleftharpoons$ & OH + OH \\
$\mathcal{R}_{12}$ & HO$_2$ + O      & $\rightleftharpoons$ & O$_2$ + OH \\
$\mathcal{R}_{13}$ & HO$_2$ + OH     & $\rightleftharpoons$ & H$_2$O + O$_2$ \\
$\mathcal{R}_{14}$ & HO$_2$ + HO$_2$ & $\rightleftharpoons$ & H$_2$O$_2$ + O$_2$ \\
$\mathcal{R}_{15}$ & H$_2$O$_2$ + M  & $\rightleftharpoons$ & OH + OH + M \\
$\mathcal{R}_{16}$ & H$_2$O$_2$ + H  & $\rightleftharpoons$ & H$_2$O + OH \\
$\mathcal{R}_{17}$ & H$_2$O$_2$ + H  & $\rightleftharpoons$ & HO$_2$ + H$_2$ \\
$\mathcal{R}_{18}$ & H$_2$O$_2$ + O  & $\rightleftharpoons$ & OH + HO$_2$ \\
$\mathcal{R}_{19}$ & H$_2$O$_2$ + OH & $\rightleftharpoons$ & HO$_2$ + H$_2$O \\
\bottomrule
\end{tabular}
\end{center}
\caption{Reaction mechanism for H$_2$/O$_2$ from~\cite{Yetter:1991}}.
\label{tab:kinetics}
\end{table}

The reaction rate for the $i^{th}$ reaction as a function of temperature
is given as follows:
\be
k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT), 
\label{eq:rate}
\ee
%
where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$ is the
activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
universal gas constant. 
The TChem~\cite{Safta:2011} software package is used to model homogeneous
ignition at constant pressure for a range of initial conditions for the
fuel-oxidizer mixture. During the simulation, the fuel-oxidizer mixture goes 
through a radical build-up phase followed by a sharp increase in temperature
as heat is released during the thermal runaway. We focus on quantifying the 
uncertainty in the \emph{ignition delay} due to uncertainty associated 
with the pre-exponent, $A_i$, for each reaction. The ignition delay 
is defined as the inflection point on the temperature profile during the thermal
runaway. The total number of uncertain parameters in the
present case is 19.  The $A_i$'s are considered to be uniformly distributed in
the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$; $A_i^\ast$ being the nominal
estimate corresponding to the $i^{th}$ reaction.
The set of nominal values used in the computations, for parameters 
in~\eqref{eq:rate} are provided
in~\cite{Yetter:1991}.

While the dimensionality of the problem is relatively moderate,
constructing a surrogate in the 19-dimensional parameter space could still be
expensive. Hence, we explore the possibility of constructing a
reduced-space surrogate (RSS) using the framework presented 
in section~\ref{sec:method}. 
In the present study, we focus on two scenarios: fuel(H$_2$)-rich, and
fuel(H$_2$)-lean. Consider the global reaction:
%
\be
2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2\text{O}
\label{eq:global}
\ee 
%
The equivalence ratio $\phi$ is defined as follows:
%
\be
\phi = \frac{(M_{\text{H}_2}/M_{\text{O}_2})_\text{obs}}{(M_{\text{H}_2}/M_{\text{O}_2})_\text{st}}
\label{eq:phi}
\ee
%
The numerator in the right-hand-side represents the observed (obs) fuel-oxygen
mass ratio at a given condition and the denominator represents the
stoichiometric (st) ratio of the same quantity. Hence, $\phi$ = 1 at
stoichiometric conditions. The equivalence ratio can be altered by changing the
amount of O$_2$ in the mixture. In the case of a lean
mixture,~\eqref{eq:global} can be written as follows:
%
\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\text{H}_2\text{O} + (\alpha-1)\text{O}_2 
\hspace{3mm} (\alpha>1)
\label{eq:lean}
\ee 
%
Similarly, for the case when the mixture if fuel rich,~\eqref{eq:global} is modified
as follows:
%
\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\alpha\text{H}_2\text{O} + 2(1-\alpha)\text{H}_2
\hspace{3mm} (\alpha<1)
\label{eq:rich}
\ee 
%
Eqs.~\eqref{eq:lean} and~\eqref{eq:rich} can be generalized as follows:
%
\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\min(1,\alpha)\text{H}_2\text{O} + 
\max(\alpha-1,0)\text{O}_2 + \max(0,2-2\alpha)\text{H}_2
\label{eq:gen}
\ee 
%
From the above set of chemical equations, the relationship between $\phi$
and $\alpha$ can be easily obtained as $\phi~=~\frac{1}{\alpha}$.
Since $\phi>1$ corresponds to a rich mixture, and $\phi<1$ corresponds to a
lean mixture, we consider $\phi$ = 2.0 and 0.5 to investigate the two scenarios
respectively.

@@

\rebut{
\subsection{Comparative cost analysis}
\label{sub:cost}

In this section, we perform a comparative analysis of the computational cost
associated with obtaining converged estimates of parametric sensitivities
using DGSM, and the total-effect Sobol' indices ($\mathcal{T}(\theta_i)$). The former is computed
using the parameter screening algorithm (Algorithm~\ref{alg:screen}), and the latter is
estimated analytically by constructing a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
using a PCE has been shown to be more efficient compared to sampling 
techniques~\cite{Crestaux:2009,BlatmanSudret10}.
Moreover, a sparse-basis PCE requires fewer training points which
enhances computational savings~\cite{Sudret:2008,Blatman:2009}. 
To investigate the impact of the dimensionality, the
analysis is performed with 19 uncertain parameters, i.e.
the pre-exponents~($A_i$'s) as discussed earlier in~\ref{sub:setup} and~\ref{sub:imp}, and
33 uncertain parameters wherein the activation energies~($E_{a,i}$'s) are considered to
be uncertain in addition to the $A_i$'s. The $E_{a,i}$'s are also considered to be uniformly distributed in the
interval: [$0.9E_{a,i}^\ast,1.1E_{a,i}^\ast$], where $E_{a,i}^\ast$ is the nominal value
for the $i^\text{th}$ reaction as provided in~\cite{Yetter:1991}. Note that only those
$E_{a,i}$'s with a non-zero nominal value are considered as uncertain, and therefore the
total number of uncertain parameters in the high-dimensional case is 33 as opposed to 38.

@@

Before comparing the computational cost pertaining to the two approaches (DGSM-based and 
Sobol'-based) and the impact of dimensionality, we verify that the parametric sensitivities are
consistent in both cases. Sensitivity estimates for the 33 uncertain parameters obtained
using the DGSM-based strategy, and by evaluating $\mathcal{T}(\theta_i)$ analytically
using the sparse-basis PCE are plotted and placed adjacent to each other for comparison
in Figure~\ref{fig:sense33D}.
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.42\textwidth]{./Figures/ub33D}
  \includegraphics[width=0.40\textwidth]{./Figures/sens_kinetics33D}
\caption{
Left: Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), 
obtained using $N$ = 5, 10 samples in the full parameter space; and
Right: Total-effect Sobol' indices, $\mathcal{T}(\theta_i)$ for the 33 uncertain rate-controlling
parameters ($A_i$'s and $E_{a,i}$'s).}
\label{fig:sense33D}
\end{center}
\end{figure}
%
The plots clearly indicate that the relative importance of the uncertain parameters is
consistent in both cases. Specifically, both approaches reveal that the uncertainty in
the ignition delay is predominantly due to the uncertainty in $E_{a,1}$ and $E_{a,10}$ with a 
minor contribution from $E_{a,12}$, whereas, contributions from other parameters is either zero
or negligible. These results are clearly indicative of the potential for dimension reduction in this
case using the proposed sensitivity-driven approach. A reasonably accurate RSS in a 2D
parameter space could potentially capture the uncertainty in the ignition delay due to the
uncertainty in the 33 rate-controlling parameters.

The computational cost is estimated in terms of the number of function evaluations or model runs,
denoted by $\mathcal{M}$ in each case. In the case of DGSM-based approach presented in this work, 
$\mathcal{M}$ = $N(N_p+1)$ ($N$: number of samples, $N_p$: number of parameters)
as discussed earlier in~\ref{sub:dgsm}. In the case of PCE-based computation of $\mathcal{T}(\theta_i)$,
$\mathcal{M}$ is the sum total of the number of training points used for constructing the sparse-basis
PCE and the number of evaluations used for its verification. In Table~\ref{tab:cost},
we provide a comparison of $\mathcal{M}$ for the two approaches in the case of 19 and 33 uncertain
parameters for the H$_2$/O$_2$ reaction kinetics application. 
%
\begin{table}[htbp]
\renewcommand{\arraystretch}{1.5}
\caption{A comparison of computational cost for the DGSM-based and Sobol'-based parametric 
sensitivity analysis in the case of 19 and 33 uncertain rate-controlling parameters.}
\begin{center}
\begin{tabular}{c|p{4cm}|p{4cm}|}
\cline{2-3}
& \multicolumn{2}{ c| }{$\mathbf{\#}$ \textbf{of Function Evaluations/Model Runs}~($\mathcal{M}$)} \\ \cline{2-3} 
& \centering \textbf{19D} & \hspace{18mm} \textbf{33D} \\  \hhline{===}
\multicolumn{1}{ |l|| }{\textbf{DGSM-based}, 
$\widehat{\mathcal{C}_i\mu_i}$} & \centering 100 + $N_{v_1}$ & \hspace{13mm} 170 + $N_{v_1}$ \\ 
\cline{1-3}
\multicolumn{1}{ |l|| }{\textbf{Total-effect Sobol'}, $\mathcal{T}(\theta_i)$} & \centering 20 + $N_{v_2}$ & 
\hspace{13mm} 500 + $N_{v_2}$ \\ \cline{1-3}  
\end{tabular}
\end{center}
\label{tab:cost}
\end{table}
%
For the 19D case, estimating the converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$)
required 5 samples. However, since finite difference was used in this work for estimating the gradient of the
model output, a total of 100 model runs were required. Additionally, the screening procedure is continued for
one iteration using $N$ = 10 samples to ensure the convergence of $\widehat{\mathcal{C}_i\mu_i}$.
Since these additional runs are essentially used for verification, we denote them as $N_{v_1}$.
%As mentioned earlier in~\ref{sub:dgsm}, depending
%upon the application, it is possible to explore efficient techniques for gradient estimation such as those involving 
%adjoint computation and automatic differentiation. Hence, there is scope for a significant
%reduction in the computational cost
%associated with the DGSM-based approach. 
On the other hand, constructing the sparse-basis PCE requires only 20 samples in
the 19D parameter space with uncertain pre-exponents. Additional model runs ($N_{v_2}$)
 typically ranging from
$\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$ are needed to build a cross validation test suite to verify the 
accuracy of the PCE.  
The DGSM-based approach could thus yield computational gains especially when 
efficient gradient computation techniques are used. The comparison is significantly more favorable for the 
proposed DGSM-based framework in the higher dimensional case involving 33 uncertain parameters. 
Once again, converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) are obtained
using only 5 samples in the 33D parameter space. For verification, the screening procedure is
continued for one iteration by evaluating the model output at 10 samples in 33 dimensions. 
Therefore, a total of 340 model runs are needed in this case
including for gradient computation using finite difference as well as verification. Whereas, as discussed earlier,
constructing the sparse PCE itself requires model runs at 500 training points to sufficiently converge. Additional
model runs ($\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$) are required to further verify the accuracy of the 
resulting PCE. Note that the analysis was performed
for the fuel-rich case. However, similar trends are expected for the fuel-lean case and we do not include them here
for brevity.

Based on our findings, it appears that the proposed DGSM-based approach can offer a significant
computational advantage especially in higher dimensions due to multiple factors: (1) Computational
effort required for estimating $\mathcal{T}(\theta_i)$ is observed to increase substantially with dimensionality even
when using sparse-basis PCEs. Whereas, the DGSM-based estimates converge
with only a few samples ($N$ = 5) even for a relatively higher-dimensional case. Moreover, it must be noted that
the computational gains associated with the proposed DGSM-based approach could be enhanced
significantly by employing efficient gradient computation techniques such as those involving adjoints
and automatic differentiation as mentioned earlier in~\ref{sub:dgsm}; (2) The number of model runs
needed to verify the convergence of $\widehat{\mathcal{C}_i\mu_i}$ can be controlled
using the iterative strategy in this work
and is expected to be much smaller than the number of runs needed for verifying the accuracy of  
$\mathcal{T}(\theta_i)$ especially in high-dimensional settings. Specifically, for the 33D case,
model runs at 5 additional samples (corresponding to the first iteration) were used to verify the
convergence of $\widehat{\mathcal{C}_i\mu_i}$ as opposed to 1000 model evaluations used to verify
the accuracy of the PCE. 
It can thus be understood that for higher dimensional problems involving hundreds of 
parameters, conventional approaches (even sparse-basis PCEs) can quickly become prohibitive and
the proposed DGSM-based approach could help
reduce the computational effort by several orders of magnitude.

>>>>

\subsection{Problem Setup}
\label{sub:setup}  
The mechanism comprises of 19 reactions including chain reactions,
dissociation/recombination reactions, and formation and consumption
of intermediate species as provided below in Table~\ref{tab:kinetics}.
%
\begin{table}[htbp]
\renewcommand*{\arraystretch}{1.2}
\begin{center}
\begin{tabular}{llll}
\toprule
Reaction \#     & Reaction &&\\
\bottomrule
$\mathcal{R}_1$ & H + O$_2$          & $\rightleftharpoons$ & O + OH \\
$\mathcal{R}_2$ & O + H$_2$          & $\rightleftharpoons$ & H + OH \\
$\mathcal{R}_3$ & H$_2$ + OH         & $\rightleftharpoons$ & H$_2$O + H \\
$\mathcal{R}_4$ & OH + OH            & $\rightleftharpoons$ & O + H$_2$O \\
$\mathcal{R}_5$ & H$_2$ + M          & $\rightleftharpoons$ & H + H + M \\
$\mathcal{R}_6$ & O + O + M          & $\rightleftharpoons$ & O$_2$ + M \\
$\mathcal{R}_7$ & O + H + M          & $\rightleftharpoons$ & OH + M \\
$\mathcal{R}_8$ & H + OH +M          & $\rightleftharpoons$ & H$_2$O + M \\
$\mathcal{R}_9$ & H + O$_2$ + M      & $\rightleftharpoons$ & HO$_2$ + M \\
$\mathcal{R}_{10}$ & HO$_2$ + H      & $\rightleftharpoons$ & H$_2$ + O$_2$ \\
$\mathcal{R}_{11}$ & HO$_2$ + H      & $\rightleftharpoons$ & OH + OH \\
$\mathcal{R}_{12}$ & HO$_2$ + O      & $\rightleftharpoons$ & O$_2$ + OH \\
$\mathcal{R}_{13}$ & HO$_2$ + OH     & $\rightleftharpoons$ & H$_2$O + O$_2$ \\
$\mathcal{R}_{14}$ & HO$_2$ + HO$_2$ & $\rightleftharpoons$ & H$_2$O$_2$ + O$_2$ \\
$\mathcal{R}_{15}$ & H$_2$O$_2$ + M  & $\rightleftharpoons$ & OH + OH + M \\
$\mathcal{R}_{16}$ & H$_2$O$_2$ + H  & $\rightleftharpoons$ & H$_2$O + OH \\
$\mathcal{R}_{17}$ & H$_2$O$_2$ + H  & $\rightleftharpoons$ & HO$_2$ + H$_2$ \\
$\mathcal{R}_{18}$ & H$_2$O$_2$ + O  & $\rightleftharpoons$ & OH + HO$_2$ \\
$\mathcal{R}_{19}$ & H$_2$O$_2$ + OH & $\rightleftharpoons$ & HO$_2$ + H$_2$O \\
\bottomrule
\end{tabular}
\end{center}
\caption{Reaction mechanism for H$_2$/O$_2$ from~\cite{Yetter:1991}}.
\label{tab:kinetics}
\end{table}
%
The reaction rate for the $i^{th}$ reaction as a function of temperature
is given as follows:
\be
k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT), 
\label{eq:rate}
\ee
%
where $A_i$, $n_i$, and $E_{a,i}$ denote the pre-exponent, the index of $T$, and
and the activation energy corresponding to the $i^{th}$ reaction; and $R$ is the
universal gas constant. 
The TChem~\cite{Safta:2011} software package is used to model homogeneous
ignition at constant pressure for a range of initial conditions for the
fuel-oxidizer mixture. During the simulation, the fuel-oxidizer mixture goes 
through a radical build-up phase followed by a sharp increase in temperature
as heat is released during the thermal runaway. We focus on quantifying the 
uncertainty in the \emph{ignition delay} due to uncertainty associated 
with the pre-exponent, $A_i$, for each reaction. The ignition delay 
is defined as the inflection point on the temperature profile during the thermal
runaway. The total number of uncertain parameters in the
present case is 19.  The $A_i$'s are considered to be uniformly distributed in
the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$; $A_i^\ast$ being the nominal
estimate corresponding to the $i^{th}$ reaction.
The set of nominal values used in the computations, for parameters 
in~\eqref{eq:rate} are provided
in~\cite{Yetter:1991}.

While the dimensionality of the problem is moderate,
constructing a surrogate in the 19-dimensional parameter space could still be
expensive. Hence, we explore the possibility of constructing a
reduced-space surrogate (RSS) using the framework presented 
in section~\ref{sec:method}. 
In the present study, we focus on two scenarios: fuel(H$_2$)-rich, and
fuel(H$_2$)-lean. Consider the global reaction:
%
\be
2\text{H}_2 + \text{O}_2 \rightarrow 2\text{H}_2\text{O}
\label{eq:global}
\ee 
%
The equivalence ratio $\phi$ is defined as follows:
%
\be
\phi = \frac{(M_{\text{H}_2}/M_{\text{O}_2})_\text{obs}}{(M_{\text{H}_2}/M_{\text{O}_2})_\text{st}}
\label{eq:phi}
\ee
%
The numerator in the right-hand-side represents the observed (obs) fuel-oxygen
mass ratio at a given condition and the denominator represents the
stoichiometric (st) ratio of the same quantity. Hence, $\phi$ = 1 at
stoichiometric conditions. The equivalence ratio can be altered by changing the
amount of O$_2$ in the mixture. In the case of a lean
mixture,~\eqref{eq:global} can be written as follows:
%
\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\text{H}_2\text{O} + (\alpha-1)\text{O}_2 
\hspace{3mm} (\alpha>1)
\label{eq:lean}
\ee 
%
Similarly, for the case when the mixture if fuel rich,~\eqref{eq:global} is modified
as follows:
%
\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\alpha\text{H}_2\text{O} + 2(1-\alpha)\text{H}_2
\hspace{3mm} (\alpha<1)
\label{eq:rich}
\ee 
%
Eqs.~\eqref{eq:lean} and~\eqref{eq:rich} can be generalized as follows:
%
\be
2\text{H}_2 + \alpha\text{O}_2 \rightarrow 2\min(1,\alpha)\text{H}_2\text{O} + 
\max(\alpha-1,0)\text{O}_2 + \max(0,2-2\alpha)\text{H}_2
\label{eq:gen}
\ee 
%
From the above set of chemical equations, the relationship between $\phi$
and $\alpha$ can be easily obtained as $\phi~=~\frac{1}{\alpha}$.
Since $\phi>1$ corresponds to a rich mixture, and $\phi<1$ corresponds to a
lean mixture, we consider $\phi$ = 2.0 and 0.5 to investigate the two scenarios
respectively.

@@

\rebut{
\subsection{Comparative cost analysis: higher-dimensional setting}
\label{sub:cost}

In this section, we perform a comparative analysis of the computational cost
associated with obtaining converged estimates of parametric sensitivities
using DGSM, and the total-effect Sobol' indices ($\mathcal{T}(\theta_i)$). The former is computed
using the parameter screening algorithm (Algorithm~\ref{alg:screen}), and the latter is
estimated using a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
using a PCE has been shown to be more efficient compared to sampling 
techniques~\cite{Crestaux:2009,BlatmanSudret10}.
Moreover, a sparse-basis PCE requires fewer training points which
enhances computational savings~\cite{Sudret:2008,Blatman:2009}. 
To investigate the impact of the dimensionality, the
analysis is performed with 19 uncertain parameters, i.e.
the pre-exponents~($A_i$'s) as discussed earlier in~\ref{sub:setup} and~\ref{sub:imp}, and
33 uncertain parameters wherein the activation energies~($E_{a,i}$'s) are considered to
be uncertain in addition to the $A_i$'s. The $E_{a,i}$'s are also considered to be uniformly distributed in the
interval: [$0.9E_{a,i}^\ast,1.1E_{a,i}^\ast$], where $E_{a,i}^\ast$ is the nominal value
for the $i^\text{th}$ reaction as provided in~\cite{Yetter:1991}. Note that only those
$E_{a,i}$'s with a non-zero nominal value are considered as uncertain, and therefore the
total number of uncertain parameters in the high-dimensional case is 33 as opposed to 38.

@@

Before comparing the computational cost pertaining to the two approaches (DGSM-based and 
Sobol'-based) and the impact of dimensionality, we verify that the parametric sensitivities are
consistent in both cases. Sensitivity estimates for the 33 uncertain parameters obtained
using the DGSM-based strategy, and by evaluating $\mathcal{T}(\theta_i)$ 
using the sparse-basis PCE are plotted and placed adjacent to each other for comparison
in Figure~\ref{fig:sense33D}.
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.42\textwidth]{./Figures/ub33D}
  \includegraphics[width=0.40\textwidth]{./Figures/sens_kinetics33D}
\caption{
Left: Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), 
obtained using $N$ = 5, 10 samples in the full parameter space; and
Right: Total-effect Sobol' indices, $\mathcal{T}(\theta_i)$ for the 33 uncertain rate-controlling
parameters ($A_i$'s and $E_{a,i}$'s).}
\label{fig:sense33D}
\end{center}
\end{figure}
%
The plots clearly indicate that the relative importance of the uncertain parameters is
consistent in both cases. Specifically, both approaches reveal that the uncertainty in
the ignition delay is predominantly due to the uncertainty in $E_{a,1}$ and $E_{a,10}$ with a 
minor contribution from $E_{a,12}$, whereas, contributions from other parameters is either zero
or negligible. These results are clearly indicative of the potential for dimension reduction in this
case using the proposed sensitivity-driven approach. A reasonably accurate RSS in a 2D
parameter space could potentially capture the uncertainty in the ignition delay due to the
uncertainty in the 33 rate-controlling parameters.

The computational cost is estimated in terms of the number of function evaluations or model runs,
denoted by $\mathcal{M}$ in each case. In the case of DGSM-based approach presented in this work, 
$\mathcal{M}$ = $N(N_p+1)$ ($N$: number of samples, $N_p$: number of parameters)
as discussed earlier in~\ref{sub:dgsm}. In the case of PCE-based computation of $\mathcal{T}(\theta_i)$,
$\mathcal{M}$ is the sum total of the number of training points used for constructing the sparse-basis
PCE and the number of evaluations used for its verification. In Table~\ref{tab:cost},
we provide a comparison of $\mathcal{M}$ for the two approaches in the case of 19 and 33 uncertain
parameters for the H$_2$/O$_2$ reaction kinetics application. 
%
\begin{table}[htbp]
\renewcommand{\arraystretch}{1.5}
\caption{A comparison of computational cost for the DGSM-based and Sobol'-based parametric 
sensitivity analysis in the case of 19 and 33 uncertain rate-controlling parameters.}
\begin{center}
\begin{tabular}{c|p{4.2cm}|p{4.2cm}|}
\cline{2-3}
& \multicolumn{2}{ c| }{$\mathbf{\#}$ \textbf{of Function Evaluations/Model Runs}~($\mathcal{M}$)} \\ \cline{2-3} 
& \centering \textbf{19D} & \hspace{18mm} \textbf{33D} \\  \hhline{===}
\multicolumn{1}{ |l|| }{$\widehat{\mathcal{C}_i\mu_i}$ (\textbf{DGSM-based)}} & \centering 5(19+1) = 100 + $N_{v_1}$ & \hspace{3mm} 5(33+1) = 170 + $N_{v_1}$ \\ 
\cline{1-3}
\multicolumn{1}{ |l|| }{$\mathcal{T}(\theta_i)$ (\textbf{PCE-based})} & \centering 20 + $N_{v_2}$ & 
\hspace{13mm} 500 + $N_{v_2}$ \\ \cline{1-3}  
\end{tabular}
\end{center}
\label{tab:cost}
\end{table}
%
For the 19D case, estimating the converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$)
required 5 samples. However, since finite difference was used in this work for estimating the gradient of the
model output, a total of 100 model runs were required. Additionally, the screening procedure is continued for
one iteration using $N$ = 10 samples to ensure the convergence of $\widehat{\mathcal{C}_i\mu_i}$.
Since these additional runs are essentially used for verification, we denote them as $N_{v_1}$.
%As mentioned earlier in~\ref{sub:dgsm}, depending
%upon the application, it is possible to explore efficient techniques for gradient estimation such as those involving 
%adjoint computation and automatic differentiation. Hence, there is scope for a significant
%reduction in the computational cost
%associated with the DGSM-based approach. 
On the other hand, constructing the sparse-basis PCE requires only 20 samples in
the 19D parameter space with uncertain pre-exponents. Additional model runs ($N_{v_2}$)
 typically ranging from
$\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$ are needed to build a cross validation test suite to verify the 
accuracy of the PCE.  
The DGSM-based approach could thus yield computational gains especially when 
efficient gradient computation techniques are used. The comparison is significantly more favorable for the 
proposed DGSM-based framework in the higher dimensional case involving 33 uncertain parameters. 
Once again, converged estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) are obtained
using only 5 samples in the 33D parameter space. For verification, the screening procedure is
continued for one iteration by evaluating the model output at 10 samples in 33 dimensions. 
Therefore, a total of 340 model runs are needed in this case
including for gradient computation using finite difference as well as verification. Whereas, as discussed earlier,
constructing the sparse PCE itself requires model runs at 500 training points to sufficiently converge. Additional
model runs ($\mathcal{O}(10^{2})$ - $\mathcal{O}(10^{3})$) are required to further verify the accuracy of the 
resulting PCE. Note that the analysis was performed
for the fuel-rich case.

Based on our findings, it appears that the proposed DGSM-based approach can offer a significant
computational advantage especially in higher dimensions due to multiple factors: (1) Computational
effort required for estimating $\mathcal{T}(\theta_i)$ is observed to increase substantially with dimensionality even
when using sparse-basis PCEs. Whereas, the DGSM-based estimates converge
with only a few samples, $\mathcal{O}(10^1)$ even for a relatively higher-dimensional case. Moreover, it must be noted that
the computational gains associated with the proposed DGSM-based approach could be enhanced
significantly by employing efficient gradient computation techniques such as those involving adjoints
and automatic differentiation as mentioned earlier in~\ref{sub:dgsm}; (2) The number of model runs
needed to verify the convergence of $\widehat{\mathcal{C}_i\mu_i}$ can be controlled
using the iterative strategy in this work
and is expected to be much smaller than the number of runs needed for verifying the accuracy of  
$\mathcal{T}(\theta_i)$ especially in high-dimensional settings. Specifically, for the 33D case,
model runs at 5 additional samples (corresponding to the first iteration) were used to verify the
convergence of $\widehat{\mathcal{C}_i\mu_i}$ as opposed to 1000 model evaluations used to verify
the accuracy of the PCE. 
It can thus be understood that for higher dimensional problems involving hundreds of 
parameters, conventional approaches (even sparse-basis PCEs) can quickly become prohibitive and
the proposed DGSM-based approach could help
reduce the computational effort by several orders of magnitude.
